Stochastic Blockmodels for Relational Event Data

### 2012-05-02 docs/submission.tex
Edits to split/merge description.

>>>>

Since the proposed split vectors $\phi^s$ are close the $\phi^m$, this has a higher probability than the split states having arisen from the proposed merge state, which is closer to the midpoint between the two $\phi^s$ vectors.  This increases the acceptance probability for splits (and decreases the probability of merges).  However, the probability of getting assigned to each cluster (through the restricted Gibbs scan) might balance things out.
